Cluster Difference Imaging Photometric Survey (CDIPS) II: A Jupiter-Sized Planet in IC~2602

### 2020-05-08 paper/ms.tex
update paper

@@

Figure~\ref{fig:sed}.

@@

\subsection{Validation of \pn}

>>>>

do a 5 subplot olympic arrangement...

plx vs pmdec
plx vs pmra
pmdec vs pmra
plx vs rv
ra vs dec

(or could just do 2 3d plots... one of positions, one of velocities. i
like this idea best, tbh.).

...
OR could do it as a corner plot, 6 dimensions...

ra
dec
plx
pmra
pmdec
rv

this would be sicker.

\subsubsection{HR Diagram}
\begin{figure*}[t!]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f7.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ 
  {\bf Hertzsprung-Russell diagram of \tn\ and members of \cn.}
  Members (black circles) were identified by
  \citet{cantatgaudin_gaia_2018}.  Gray circles are non-member stars
  within 5 standard deviations of the mean \cn\ right ascension,
  declination, and parallax.  $G$ denotes Gaia broadband magnitudes,
  $Bp$ Gaia blue, $Rp$ Gaia red, and $\omega_{\rm as}$ the parallax in
  arcseconds. 
  \label{fig:hr}
	}
\end{figure*}

Figure~\ref{fig:hr} shows a Hertzsprung-Russell diagram of \tn\ in
reference to the broader \cn\ cluster, as well as its neighborhood.
Cluster members were identified by \citet{cantatgaudin_gaia_2018}
using using Gaia-DR2 positions, proper motions, and parallaxes.  
We included candidate members with formal membership probability
exceeding 10\%.  Save for a few low-mass outliers, most members appear
to be young and coeval.

\tn\ is in its expected position relative to the other members along
the cluster isochrone.  This photometrically limits the presence of
binary companions in \tn\ system, to a magnitude difference of perhaps
half the brightness of the target star.

Figure~\ref{fig:hr} also shows that the membership census of \cn\ is
likely incomplete.  We defined the reference ``neighborhood'' as the
group of at most $10^4$ randomly selected non-member stars within 5
standard deviations of the mean \cn\ 1 right ascension, declination,
and parallax.  We queried Gaia DR2 for these stars using
\texttt{astroquery} \citep{astroquery_2018}.  Many low-mass stars
appear above the main sequence, even though they were not identified
as 5-dimensional kinematic members through the unsupervised
\citet{cantat-gaudin_gaia_2018} membership assignment process.

@@

From CHIRON spectra, my current best guess spectroscopic parameters
 are as follows.
 Teff = 5946 +/- 39
 logg = 4.48 +/- 0.03
 feh = -0.065 +/- 0.035
 vsini = 17.48 +/- 0.15

Figure~\ref{fig:sed}.
The SED fit, looking really good with rchi2 = 1.6:

The fit parameters are: 
Av = 0.20 +/- 0.03
Fbol = 1.967 +/- 0.046 e-9 erg/s/cm2 
Rstar = 1.049 +/- 0.019 Rsun

From the spectroscopic logg and the above Rstar, we get an independent
mass estimate of 
Mstar = 1.21 +/- 0.10 Msun 
At face value, the mass seems a bit high for the radius, but I'm
guessing that just means the spectroscopic logg is a bit too high.

@@

\subsection{Validation of \pn}
\label{subsec:validation}
